\documentclass[12pt, a4paper]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[a4paper, portrait, margin=1in]{geometry}

\newcommand{\F}{\mathbb{F}}
\renewcommand{\qedsymbol}{$\blacksquare$}

\newtheorem{theorem}{Theorem}

% let's begin
\begin{document}

\noindent\textbf{(Q3)}

\begin{theorem}
    Let $\F = \{1, 0, a, b\}$ be a field with 4 distinct elements.

    Given that $ab = 1$, prove that $a^2 = b$.
\end{theorem}

\begin{proof}
    We observe that by the Multiplicative Inverse Axiom, $a$ and $b$ are reciprocals
    of each other. Thus, it follows that:

    \[
        ab = 1 \implies b = a^{-1}
    \]

    We also observe that $a^2$ is simply $a \cdot a$.

    We can prove this theorem by a process of elimination. We try all possible values
    of $a \cdot a$, and eliminate those that violate the the definition of a field
    or its axioms.

    First we consider $a \cdot a = 0$. It follows that:

    \[
        a^{-1} \cdot a \cdot a = 0 \cdot a^{-1} \implies a = 0
    \]

    Which is not allowed, as $a$ and $0$ have to be distinct elements of $\F$.

    Next, considering $a \cdot a = a$, it again follows:

    \begin{align*}
        a \cdot a & = a \\
        \implies a^{-1} \cdot a \cdot a & = a \cdot a^{-1}\\
        \implies a & = 1
    \end{align*}
    Which is also not allowed for the same reason.

    Next, considering $a \cdot a = 1$, it follows:
    \begin{align*}
        a \cdot a & = 1\\
        \implies a^{-1} \cdot a \cdot a & = 1 \cdot a^{-1}\\
        \implies a = a^{-1} & = b
    \end{align*}
    Which is also not allowed, again for the same reason.

    This leaves $a \cdot a = b$ as the final option, so it has to be correct.

    To confirm this, we can subject this to the same process:

    \begin{align*}
        a \cdot a & = b\\
        \implies a^{-1} \cdot a \cdot a & = a^{-1} \cdot b\\
        \implies a & = b \cdot b = b^{2}
    \end{align*}

    Since $b$ is a distinct element in $\F$, this holds under the definition of a field.

\end{proof}

\end{document}